\Large{Learning to Pivot with Adversarial Networks}

### 2016-11-02 tex/paper.tex
typo

If $Z$ takes discrete values, then $p_{\theta_r}$ can be represented e.g. as a
probabilistic classifier $\mathbb{R} \mapsto \mathbb{R}^{|{\cal Z|}}$ whose
output $j$ (for $j=1, \dots, |{\cal Z}|$) is the estimated probability mass
$p_{\theta_r}(z_j|f(X;\theta_f)=s)$. Similarly, if $Z$ takes continuous values and
if we assume a flexible enough parametric distribution ${\cal P}$ for $Z|f(X;\theta_f)=s$
(e.g., a mixture of gaussians, as modeled with a mixture
density network~\citep{bishop1994mixture}), then $p_{\theta_r}$ can be
represented e.g. as a network whose output $j$ is the estimated value of the
corresponding parameter $\gamma_j$ of that distribution (e.g., the mean,
variance and mixing coefficients of its components). As in
\citep{nix1994estimating,bishop1994mixture}, the estimated probability density
$p_{\theta_r}(z|f(X;\theta_f)=s)$ can then be evaluated for any $z \in {\cal Z}$ and any score $s \in {\cal S}$.
As further explained in the next section, let us note that the adversary $r$ may
take any form, i.e. it does need to be a neural network, as long as it exposes a
differentiable function $p_{\theta_r}(z|f(X;\theta_f)=s)$ of sufficient capacity
to represent the true distribution.

>>>>

If $Z$ takes discrete values, then $p_{\theta_r}$ can be represented e.g. as a
probabilistic classifier $\mathbb{R} \mapsto \mathbb{R}^{|{\cal Z|}}$ whose
output $j$ (for $j=1, \dots, |{\cal Z}|$) is the estimated probability mass
$p_{\theta_r}(z_j|f(X;\theta_f)=s)$. Similarly, if $Z$ takes continuous values and
if we assume a flexible enough parametric distribution ${\cal P}$ for $Z|f(X;\theta_f)=s$
(e.g., a mixture of gaussians, as modeled with a mixture
density network~\citep{bishop1994mixture}), then $p_{\theta_r}$ can be
represented e.g. as a network whose output $j$ is the estimated value of the
corresponding parameter $\gamma_j$ of that distribution (e.g., the mean,
variance and mixing coefficients of its components). As in
\citep{nix1994estimating,bishop1994mixture}, the estimated probability density
$p_{\theta_r}(z|f(X;\theta_f)=s)$ can then be evaluated for any $z \in {\cal Z}$ and any score $s \in {\cal S}$.
As further explained in the next section, let us note that the adversary $r$ may
take any form, i.e. it does not need to be a neural network, as long as it exposes a
differentiable function $p_{\theta_r}(z|f(X;\theta_f)=s)$ of sufficient capacity
to represent the true distribution.
